Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Overleaf 2022 01 20 2159 (#13)
* Updates from Overleaf

* Shorted conclusion
Fix typo

%2. Entrée/Sortie
\textbf{NER Stage.} The second stage of the pipeline aims an extracting the named entities from a text with a NER
system. This text originates from the OCR outputs in a real-word scenario but might be groundtruth text in order to
evaluate the NER performance standalone. There are 5 type of entity to detect~(see.~\cref{tab.entities}).
The NER system has to classify non-overlapping parts of the text into one of these entity (or none of them). A second
Q.A. (namely NER Q.A.) is performed at the end of this stage between the groundtruth and the NER output.

Note that the dataset used to assess the NER stage is subset of the entries. Indeed, we need to ensure that the datasets
contain the same entries whichever the OCR used in the previous stage. Entries where the OCR produced an empty string
and those for which no entity could be projected from the groundtruth have to be ignored. We filter the set of entries by
keeping only the entries that are always valid at the end of the stage 1. At the cost of losing 5\% of the references
entries, we thus have 8341 valid entries at the input of the stage 2.

>>>>

%2. Entrée/Sortie
\textbf{NER Stage.} The second stage of the pipeline aims an extracting the named entities from a text with a NER
system. This text originates from the OCR outputs in a real-word scenario but might be the groundtruth text in order to
evaluate the NER performance independently. There are 5 type of entity to detect~(see.~\cref{tab.entities}).
The NER system has to classify non-overlapping parts of the text into one of these entity (or none of them). A second
Q.A. (namely NER Q.A.) is performed at the end of this stage between the groundtruth and the NER output.

Note that the dataset used to assess the NER stage is a subset of the entries. Indeed, we need to ensure that the datasets
contain the same entries whichever the OCR used in the previous stage. Entries where the OCR produced an empty string
and those for which no entity could be projected from the groundtruth have to be ignored. We filter the set of entries by
keeping only the entries that are always valid at the end of the stage 1. At the cost of losing 5\% of the references
entries, we thus have 8341 valid entries at the input of the stage 2.
